Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-10-25 ms.tex
more text describing the GL dewar tests

\clearpage
\subsection{GL Dewar Tests}

The GL dewar, located at the University of Arizona, is a laboratory setup for assessing NIRCam flight and spare detectors.
The key difference with the Asic dewar discussed below is that the detector readout electronics are completely different, using a Leach system that is operated outside of the dewar as opposed to the Asic, which is lives right next to the detectors at cryogenic temperatures.
The GL dewar detector stability tests are helpful in isolating noise sources that arise from the detectors versus the readout electronics.

An LED illumination source flood-illuminates the detectors and the arrays are read out in subarray mode to create time series.
Figure \ref{fig:GLtSeries} shows the detector subarray illumination as well as two apertures that were used for time series photometry.
The first handful of frames show an initial ``warmup" period lasting about 9 seconds.
This quickly stabilizes to a 1200 ppm standard deviation likely dominated by lamp variations.
If one divides the two apertures by each other, the resulting time series is very flat and stable to within 260 ppm.
As with the Asic dewar, we find very good performance when comparing two apertures within the same detector.
This can be the result of common-mode systematic errors that divide out, so it is also important to check the time series against an independent detetor.

\begin{figure*}
\gridline{\fig{ap_labels_S02illum_GLrun104.pdf}{0.32\textwidth}{Apertures}
		\fig{raw_tser_phot_S02illum1miAll_GLrun104.pdf}{0.32\textwidth}{Raw time series}
		\fig{refcor_phot_S02illum1miAll_GLrun104.pdf}{0.32\textwidth}{Ratio Time Series}}
\caption{Two photometric apertures are placed on the subarray, where they both see common-mode variations in the lamp.
The ratio of the time series of each aperture shows a handful of integrations at the beginning that stand out, which quickly stabilize to the 240 ppm level.
}\label{fig:GLtSeries}
\end{figure*}

@@

\subsubsection{Across Detectors}
We also examine the time series across detectors from ``Run104''.
This approach will test whether there are systematics unique to each detector/readout electronics.
We compare aperture photometry on the S02 versus S03 detector with background subtraction.
The resulting time series are shown in Figure \ref{fig:GLtSeriesAcrossDetectors}.
We do not approach the noise levels interesting to the exoplanet noise regime.

@@

\subsection{Run 112 - Subarray 4}
We also investigate a slightly longer time series for GL dewar.

@@

\begin{figure*}
\gridline{\fig{all_var_gl_dewar_run112_sub4_hi4_no_backsub_removelinear_False_2.pdf}{0.48\textwidth}{Allan variance diagram no background subtraction}
\fig{all_var_gl_dewar_run112_sub4_hi4_with_backsub_removelinear_False_2.pdf}{0.48\textwidth}{Allan variance diagram with background subtraction}}
\caption{Allans for background-subtracted rectangular photometry on the S02 and S03 detectors.
The ratio of the two detectors' fluxes, after background subtraction, scales like $\sqrt{N}$ statistics down to the 200 ppm level, but how it works on longer timescales is not yet known.}\label{fig:GLAllanVarianceAcrossDetectors}
\end{figure*}

\subsection{Run 112 - Subarray 6}
Subarray 6 had higher lamp current and thus higher counts and lower photon noise.
It was also important to take the ratio of S01 to S03, because this pair of detectors track each other much better than the S01 /S02.
This is surprising given that S01 is a short wavelength cutoff detector, S02 is a short wavelength cutoff detector and SO3 is a long wavelength cutoff detector.
Furthermore, the S01 and S02 detectors are powered by a different pair of cards than the S03 detector.

@@

\begin{figure*}
\gridline{\fig{all_var_azlab06_sub320_multi_exp_baseline_487_489_removelinear_True_489.pdf}{0.48\textwidth}{Allan variance for AZLab06 Long Multi-Exposure Baseline}
\fig{all_var_gl_dewar_run112_sub6_hi4_side_backsub_removelinear_True_3_det_1_3.pdf}{0.48\textwidth}{Allan variance diagram for GL Dewar Run 112 Sub 6}}
\caption{Allan variance for background-subtracted rectangular photometry on the Asic Dewar versus the GL dewar.
Both tests use $320 \times 320$ subarrays, horizontally-displaced background apertures to remove 1/f noise and divide the two best-matched detectors.
The ratio of the two detectors' fluxes, after background subtraction, scales like $\sqrt{N}$ statistics down to the 60 ppm level where it begins to peel away from the $\sqrt{N}$ curve (green line).}\label{fig:GLAllanVarianceAcrossDetectorsSub6}
\end{figure*}

>>>>

\clearpage
\subsection{GL Dewar Tests}
\begin{figure*}
\gridline{\fig{ap_labels_S02illum_GLrun104.pdf}{0.32\textwidth}{Apertures}
		\fig{raw_tser_phot_S02illum1miAll_GLrun104.pdf}{0.32\textwidth}{Raw time series}
		\fig{refcor_phot_S02illum1miAll_GLrun104.pdf}{0.32\textwidth}{Ratio Time Series}}
\caption{Two photometric apertures are placed on the subarray, where they both see common-mode variations in the lamp.
The ratio of the time series of each aperture shows a handful of integrations at the beginning that stand out, which quickly stabilize to the 240 ppm level.
}\label{fig:GLtSeries}
\end{figure*}

The GL dewar, located at the University of Arizona, is a laboratory setup for assessing NIRCam flight and spare detectors.
The key difference with the Asic dewar discussed below is that the detector readout electronics are completely different, using a Leach system that is operated outside of the dewar as opposed to the Asic, which is lives right next to the detectors at cryogenic temperatures.
Comparing the GL dewar results to the asic dewar can be helpful in isolating the source of noise sources in the NIRCam system.
If the GL dewar and asic dewar share the same types of correlated noise sources, these can be attributed to the detectors.
If the asic dewar introduces or eliminates some correlated noise sources, these can be attributed to the readout electronics.

For the GL dewar, an LED illumination source flood-illuminates the detectors and the arrays are read out in subarray mode to create time series.
Figure \ref{fig:GLtSeries} shows the detector subarray illumination as well as two apertures that were used for time series photometry.
The first handful of frames show an initial ``warmup" period lasting about 9 seconds.
This quickly stabilizes to a 1200 ppm standard deviation likely dominated by lamp variations.
If one divides the two apertures by each other, the resulting time series is very flat and stable to within 260 ppm.
As with the Asic dewar, we find very good performance when comparing two apertures within the same detector.
This can be the result of common-mode systematic errors that divide out, so it is also important to check the time series against an independent detector.

@@

We also introduce a background aperture, shown in Figure \ref{fig:GLtSeriesBacksub} to remove background variations and any amplifier offsets that could affect the flux.
The resulting time series has a smaller amplitude ``warmup'' and smaller oscillations than Figure \ref{fig:GLtSeries}.
When we divide the background-subtracted flux for each aperture by the other to make a ratio time series, the resulting noise is higher than in Figure \ref{fig:GLtSeries}.
This indicates that the background subtraction step introduces more noise than it removes when comparing the differential flux between the two apertures.
We suspect that 1/f noise in the background aperture causes this increase.
To conclude, background subtraction improves the absolute flux stability but worsens the differential flux across the apertures.
When observing an exoplanet time series, for example, scientists may wish to use one reduction technique for the absolute time series to derive the planet orbital parameters, say.
Then, when analyzing the spectrum, they may wish to use an alternate technique to assess the differential flux from one wavelength to another.

\subsubsection{Across Detectors}
We also examine the time series across detectors from ``Run104'' to test whether there are systematics unique to each detector/readout electronics.
We compare aperture photometry on the S02 versus S03 detector with background subtraction.
The resulting time series are shown in Figure \ref{fig:GLtSeriesAcrossDetectors}.
We an Allan variance diagram to show how well the flux scales like $\sqrt{N}$ statistics for $N$ integrations.
The curves track the expected $\sqrt{N}$ behavior but lie well above the theoretical read and photon noise limit.
This is likely because the 1/f noise is highly correlated within the aperture whereas the theoretical and photon noise limit assumes that the noise in each pixel is independent.
We do not quire reach the noise levels interesting to the exoplanet noise regime (30-100 ppm).

@@

\subsection{Run 112 - Subarray 4}
We also investigate a slightly longer time series for GL dewar which approaches the timescales of interest to exoplanet transit lightcurves.
Figure \ref{fig:GLtSeriesRun112} shows the flux ratio between detectors S01 and S02 for the Run 112 Subarray 4 ``Hi4'' test.
The Allan variance plot again scales like the $\sqrt{N}$ statistics but above the theoretical noise limit.

@@

\begin{figure*}
\gridline{\fig{all_var_gl_dewar_run112_sub4_hi4_no_backsub_removelinear_False_2.pdf}{0.48\textwidth}{Allan variance diagram no background subtraction}
\fig{all_var_gl_dewar_run112_sub4_hi4_with_backsub_removelinear_False_2.pdf}{0.48\textwidth}{Allan variance diagram with background subtraction}}
\caption{Allans variance for background-subtracted rectangular photometry on the S02 and S03 detectors.
The ratio of the two detectors' fluxes, after background subtraction, scales like $\sqrt{N}$ statistics down to the 200 ppm level, but how it works on longer timescales is not yet known.}\label{fig:GLAllanVarianceAcrossDetectors}
\end{figure*}

\subsection{Run 112 - Subarray 6}
Subarray 6 had higher lamp current and thus higher counts and lower photon noise, which approaches the exoplanet atmospheric feature regime (30-100 ppm).
In this test, we take the ratio of flux on one detector to the other.
This removes the lamp variations but allows the

It was also important to take the ratio of S01 to S03, because this pair of detectors track each other much better than the S01 /S02.
This is surprising given that S01 is a short wavelength cutoff detector, S02 is a short wavelength cutoff detector and SO3 is a long wavelength cutoff detector.
Furthermore, the S01 and S02 detectors are powered by a different pair of cards than the S03 detector.

@@

\begin{figure*}
\gridline{\fig{all_var_azlab06_sub320_multi_exp_baseline_487_489_removelinear_True_489.pdf}{0.48\textwidth}{Allan variance for AZLab06 Long 320 Multi-Exposure Baseline}
\fig{all_var_gl_dewar_run112_sub6_hi4_side_backsub_removelinear_True_3_det_1_3.pdf}{0.48\textwidth}{Allan variance diagram for GL Dewar Run 112 Sub 6}}
\caption{Allan variance for background-subtracted rectangular photometry on the Asic Dewar versus the GL dewar.
Both tests use $320 \times 320$ subarrays, horizontally-displaced background apertures to remove 1/f noise and divide the two best-matched detectors.
For the GL dewar, the ratio of the two detectors' fluxes (after background subtraction) scales like $\sqrt{N}$ statistics down to the $\sim$60 ppm level where it begins to peel away from the $\sqrt{N}$ curve (green line).}\label{fig:GLAllanVarianceAcrossDetectorsSub6}
\end{figure*}
